---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

```{r}
unzip("activity.zip")
myData<-read.csv("activity.csv",header=TRUE)
head(myData)
tail(myData)
```
We select the complete cases for further processing
```{r}
goodData<-complete.cases(myData$steps)

```

## What is mean total number of steps taken per day?

Summarize the steps by the date  
We exclude the values that are Not Available
```{r}
stepsPerDay<-aggregate(myData$steps, by=list(myData$date), FUN=sum,na.rm=TRUE)
```
Rename columns
```{r}
names(stepsPerDay) <- c("date", "sumSteps")
head(stepsPerDay)
hist(stepsPerDay$sumSteps,xlab="steps", main="Total Steps in a day",breaks=10)
meanStep<-mean(stepsPerDay$sumSteps)
abline(v = meanStep, lwd = 2, lty = 2,col=2)
medianStep<-median(stepsPerDay$sumSteps)
abline(v = medianStep, lwd = 2, lty = 2,col=3)
legend("topright", pch = "-", col = c("red", "green"), legend = c("mean", "median"))
```
  
Mean of the total steps
```{r}
meanStep
```
Median of the total steps
```{r}
medianStep
```
## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
