---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

```{r}
unzip("activity.zip")
myData<-read.csv("activity.csv",header=TRUE)
head(myData)
tail(myData)
```

## What is mean total number of steps taken per day?

Summarize the steps by the date  
We exclude the values that are Not Available
```{r}
stepsPerDay<-aggregate(myData$steps, by=list(myData$date), FUN=sum,na.rm=TRUE)
```
Rename columns
```{r}
names(stepsPerDay) <- c("date", "sumSteps")
head(stepsPerDay)
hist(stepsPerDay$sumSteps,xlab="steps", main="Total Steps in a day",breaks=10)
meanStep<-mean(stepsPerDay$sumSteps)
abline(v = meanStep, lwd = 2, lty = 2,col=2)
medianStep<-median(stepsPerDay$sumSteps)
abline(v = medianStep, lwd = 2, lty = 2,col=3)
legend("topright", pch = "-", col = c("red", "green"), legend = c("mean", "median"))
```
  
Mean of the total steps
```{r}
meanStep
```
Median of the total steps
```{r}
medianStep
```
## What is the average daily activity pattern?

```{r}
stepsOnTime<-aggregate(myData$steps,by=list(myData$interval),FUN=mean,na.rm=TRUE)
names(stepsOnTime) <- c("interval", "meanSteps")
str(stepsOnTime)
with(stepsOnTime,plot(interval/100,meanSteps,type="l",xlab="hours",ylab="Means of steps",main="Means of Steps in 2 month interval"))
```
  
The most "stepping" interval
```{r}
maxInt<-(subset(stepsOnTime,stepsOnTime$meanSteps==max(stepsOnTime$meanSteps)))$interval
maxInt
```
Interval in hours
```{r}
maxInt/100
```
## Imputing missing values

```{r}
goodData<-complete.cases(myData$steps)
```
Number of rows NA
```{r}
nrow(myData[!goodData,])
```
The strategy is to fill with the mean of the 5 minute interval, because is more probable  
We recall from the activity pattern what we calculate, stepsOnTime  
That is the mean of steps in the intervals of 5 minutes
```{r}
#stepsOnTime<-aggregate(myData$steps,by=list(myData$interval),FUN=mean,na.rm=TRUE)
#names(stepsOnTime) <- c("interval", "meanSteps")
```
We merge the NA data with the average data. The common field is "interval"
```{r}
replacedData<-merge(myData[!goodData,],stepsOnTime)
```
We delete the extra column with NA values
```{r}
replacedData$steps<-NULL
```
Renaming the columns and reaggarange for binding
```{r}
names(replacedData) <- c("interval", "date","steps")
replaced2<-replacedData[,c(3,2,1)]
```
Binding the good data and the replaced data
```{r}
myData2<-rbind(myData[goodData,],replaced2)
```
Now we recall the first diagram for the new dataset
```{r}
stepsPerDay2<-aggregate(myData2$steps, by=list(myData2$date), FUN=sum,na.rm=TRUE)
names(stepsPerDay2) <- c("date", "sumSteps")
hist(stepsPerDay2$sumSteps,xlab="steps", main="Total Steps in a day",breaks=10)
meanStep2<-mean(stepsPerDay2$sumSteps)
abline(v = meanStep2, lwd = 2, lty = 2,col=2)
medianStep2<-median(stepsPerDay2$sumSteps)
abline(v = medianStep2, lwd = 2, lty = 2,col=3)
legend("topright", pch = "-", col = c("red", "green"), legend = c("mean", "median"))
meanStep2
medianStep2
```

## Are there differences in activity patterns between weekdays and weekends?
